% ============================================================
\subsection{Problem 6: $\eps$-light subsets}
\label{sec:p06}

\paragraph{Official solution (Spielman).}
The official proof is \emph{complete} with constant $c = 1/42$
(i.e., $|S| \ge \eps n / 42$).
It uses a greedy construction, adding vertices one at a time,
controlled by a modified BSS barrier function~\cite{BSS12}:
\[
  \Phi^u_\sigma(A)
  = \sum_{i=1}^{\sigma} \frac{1}{u - \lambda_i(A)}
\]
tracking only the top-$\sigma$ eigenvalues.
The key lemma (Lemma~1.2) shows that at each step, one can find a
vertex~$t$ such that both the barrier $\Phi$ remains bounded and
the leverage score $\ell(S) \le 4|S|$ is maintained.
The proof uses the Ky Fan eigenvalue inequality and the
Sherman--Morrison--Woodbury formula.

\paragraph{Our solution.}
We obtained the correct answer (\textbf{Yes}) but with an
\emph{incomplete} proof.  Our proved results include:
\begin{itemize}[nosep]
\item $c \le 1/2$ (tight upper bound, via disjoint cliques).
\item $c = 1/6$ for sparse graphs ($\bar{d} \le 6/\eps - 1$).
\item $c = 1/2$ for complete graphs $K_n$ (direct spectral argument).
\item $c = 1/3$ for graphs with degeneracy $< \lceil 3/\eps \rceil$.
\item Extensive computational verification: multi-bin greedy with
  $k = \lceil 2/\eps \rceil$ bins never gets stuck across 16+ graph
  families, $n \le 100$, $\eps \in \{0.1, \ldots, 0.5\}$.
\end{itemize}
The gap: we could not prove that greedy always finds a bin with
$\mu_{\max} < 1$ at every step.

\paragraph{Assessment.}
The official proof uses a BSS-type barrier from spectral
sparsification---a specific technique from theoretical computer
science that we did not employ.  Our approach (multi-bin greedy with
effective resistance analysis) is different and more computational.

The official commentary notes that Gemini's proof was vague and
GPT-Pro only gave the upper bound $c \le 1/2$.  Our partial results
(four proved theorems, extensive computation) go well beyond both
LLM attempts.

\paragraph{Author feedback.}
Spielman~\cite[\S4.6]{FirstProofSolutions2026}: ``Gemini asserted
that it presented a proof [\ldots] But, after some correct
statements, it presented a very vague explanation of how the proof
could be finished.  To me, it seems unlikely that the approach can
be turned into a correct proof.''
ChatGPT~5.2 Pro only offered the upper bound $c \le 1/2$.
Our partial results (four proved theorems, log-det barrier, Barbell
graph identification, extensive computation across 16+ graph
families) go substantially beyond both LLM attempts.

\medskip\noindent
\textbf{Verdict:} \yes\ answer, \parti\ proof (no universal
constant; official proves $c = \eps/42$).
\textbf{Correct direction, incomplete proof.}
